### 2021-05-17 main.tex
more main

%Introduction to our specialization of PROV-DM
The specialization of PROV-DM, which was introduced by Ruscheinski et al. (2018)~\cite{Ruscheinski2018}, has been revised and refined.
For capturing provenance information of simulation studies of cellular biochemical simulation models and relating these, we are defining and using
% again, is the tense current or past? "we are defining" or "we defined"?
\begin{inparaenum}[a)]
\item specific types of entities and activities and
\item specific relations with their roles and constraints.
\end{inparaenum}
During the process of collecting provenance information from these studies, we identified these types and relations as well as information that is useful for describing them.
% I think the above sentences could be reorganized to simply things
Our final set of entities, activities, and relations is shown in Table~\ref{tab:entitiesandactivities}.
Each entity and activity has already been mentioned for provenance, modeling or documentation purposes, or experiment design of simulation studies~\cite{Ruscheinski2017, Balci2012, Yilmaz2016, Monks2018, Bergmann2014, Carusi2012, Erdemir2012, Lorig2017, Ruscheinski2018, Waltemath2011, Wilsdorf2020b}, but they have not all been used together.

>>>>

%Introduction to our specialization of PROV-DM
The specialization of PROV-DM, which was introduced by Ruscheinski et al. (2018)~\cite{Ruscheinski2018}, has been revised and refined.
For capturing provenance information of simulation studies of cellular biochemical simulation models and relating these, we are defining and using
\begin{inparaenum}[a)]
\item specific types of entities and activities and
\item specific relations with their roles and constraints.
\end{inparaenum}
During the process of collecting provenance information from the studies, we identified the types and relations as well as information that was useful for describing them.
Our final set of entities, activities, and relations is shown in Table~\ref{tab:entitiesandactivities}.
Each entity and activity has already been mentioned for provenance, modeling or documentation purposes, or experiment design of simulation studies~\cite{Ruscheinski2017, Balci2012, Yilmaz2016, Monks2018, Bergmann2014, Carusi2012, Erdemir2012, Lorig2017, Ruscheinski2018, Waltemath2011, Wilsdorf2020b}, but they have not all been used together.
